The international film industry was worth an estimated \$112 billion in 2025 \citep{grandview2026}, and has become increasingly globalized in recent decades with the rise of ``runaway productions'', whereby films originating in one country are produced in another \citep{morawetz2007}. The perceived economic value of hosting film productions such as  employment and tourism spillovers, as well as the cultural prestige of a domestic film industry, has led to a large number of countries implementing incentives to attract international productions. The effectiveness and net benefits of these schemes have been constested \citep{thom2018}. This paper asks how effectively a gravity model predicts international film production flows and whether incentives are effective at attracting international productions. The analysis applies a gravity model framework to bilateral film production flows, treating filming-location choice as a form of creative services trade between an origin country (which finances production) and a destination country (where physical filming occurs). I use filming-location data and budget data extracted from the Internet Movie Database (IMDb) to construct bilateral trade flows. I also utilise a shorter audiovisual services trade dataset as a robustness check. I use cross-sectional estimates with importer, exporter, and year fixed effects to establish the unconditional association between incentive adoption and inward production. Country-pair fixed effects specifications are then used to identify incentive effects exclusively from within-pair temporal variation.

Three main findings emerge. First, the gravity framework fits bilateral film production flows well, but the determinants differ in notable ways from those documented for goods trade. Distance elasticities are substantially smaller, common language effects are larger, and colonial ties and regional trade agreements are associated with less production rather than more. Second, incentive schemes show strong evidence of attracting international production, and weaker evidence of re-shoring film production. Cross-sectional estimates imply that incentive schemes drive approximately $18\%$ more international film productions. This reduces to roughly $9-11\%$ once country-pair fixed effects are applied but is robust across subsamples. The introduction of an incentive scheme in one country also appears to reduce the number of films made in another by $9\%$ within country pairs, although this is not corroborated by the budget data or BaTIS robustness check. Third, the timing of adoption matters but the duration of operation does not. Early adopters (pre-2005) attract $26\%$ more films and $45\%$ more production spending, while late adopters show a smaller and less precisely estimated effect. Incentives show no evidence of a compounding "cluster" effect. 

This paper makes two contributions to the literature on film production incentives. First, it is the first study to apply the gravity model of trade to international film production flows. The existing literature on incentive effectiveness focuses exclusively on the U.S. state level where many determinants of production decisions such as common language do not vary. Applying the gravity framework at the international level allows for the estimation of a larger set of factors that shape production decisions. Second, the paper offers an explicit decomposition of cross-sectional and within-pair incentive effects, providing a direct quantification of the selection component of the observed correlation between incentive adoption and inward production. This effect is estimated in parallel across two independent datasets to add robustness to the findings. 

The remainder of the paper is organised as follows. Section 2 reviews the existing literature. Section 3 describes the construction of bilateral film production flows and the assembly of standard gravity controls. Section 4 sets out the methodology. Section 5 presents the estimation results and the cross-dataset validation against BaTIS. Section 6 discusses limitations. Section 7 concludes.